Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-04 Experiments.tex

% In the batch queue,  queue time becomes dominant but, at the same time, we
% have more freedom to decide the parameters of the slot.

\subsection{Experiments}\label{sec:ngeExp}

@@

We tested  pilots  with 250, 500, 1000 and 2000 worker nodes and 2 hours
walltime. The time duration is determined by the Titan's walltime policy.
Figure~\ref{fig:weakScal1a} depicts the average pilot duration, the average
execution time of AthenaMP, and the NGE pilot overhead as function of the pilot
size.

@@

%\begin{figure}[!htb]
%        \includegraphics[width=0.4\textwidth]{./figures/NGE/weakOver1.pdf}
%    \caption{Weak scalability: average overhead by running AthenaMP on 200, 500, 1000 and 2000 nodes.}
%\label{fig:weakScal1b}
%\end{figure}

@@

% \mtnote{we dowe need to keep it below 2 hours?}\aanote{You are right. It was misleading. I Changed. Check if you like it.}

@@

% \footnote{Note that the number of events has been chosen in such a way
% that all the cores of a node run one event.}
%In this way, every core of each worker node was used to simulate one event,
%. This allows us to complete
%reducing the running time of each AthenaMP to ~$20$ minutes. % only.

We ran pilots with 256, 512, 1024 and 2048 worker nodes and 3\mtnote{2?} hours
walltime. Figure~\ref{fig:weakScal2a} depicts the average pilot duration, the
average execution time of five sequential generations of AthenaMP, and the
corresponding overhead. We observe that the difference between the two durations
is more marked than in the previous experiments. Despite this, we notice that
the growth of the overhead is consistent with the increment of the number of
tasks per node for pilots with 256, 512 and 1024 worker nodes, and less than
linear for the pilot with 2048 worker nodes.

@@

%\begin{figure}[!htb]
%        \includegraphics[width=0.4\textwidth]{./figures/NGE/weakOver2.pdf}
%    \caption{Weak scalability with multiple generations: average overhead by running AthenaMP on 256, 512, 1024 and 2048 nodes.}
%\label{fig:weakScal2b}
%\end{figure}

@@

% \mtnote{Not sure I understand this sentence}\aanote{My fault. It should
% have been seven and null or 8 and 1. It depends on how we consider the word
% sequential. anyway, to avoid confusion I changed the sentence.}.

Figure \ref{fig:strongScala}  shows the average pilot duration and the average
execution time of possibly sequential AthenaMP instances.  We  notice that the
difference between the pilot duration and the AthenaMP execution times is almost
constant for all the pilot sizes, although the overall duration of the pilot
decreases linearly with the pilot size.

@@

%
%\begin{figure}[!htb]
%        \includegraphics[width=0.4\textwidth]{./figures/NGE/strongOver.pdf}
%    \caption{Strong scalability: average overhead running AthenaMP on 256, 512, 1024 and 2048 nodes.}
%\label{fig:strongScalb}
%\end{figure}

%\subsubsection{Heterogeneous execution}
%
%The last experiment provides a proof of concept about the ability of the NGE to execute heterogeneous workload.
%In particular, we coupled the execution of AthenaMP with the execution of Gromacs to simulate molecular dynamics.
%We performed the experiment by executing at first one AthenaMP per node and then, submitting a Gromacs simulation per core. Each Gromacs simulation requires ~20 minutes.
%We tested the following pilot sizes : 8, 16, 32, 64.
%
%\begin{figure}[!htb]
%        \includegraphics[width=0.5\textwidth]{./figures/NGE/MDET.pdf}
%    \caption{Average pilot execution time against average AthenaMP execution times  for pilot sizes: 256, 512, 1024 and 2048.}
%\label{fig:strongScala}
%\end{figure}
%\begin{figure}[!htb]
%        \includegraphics[width=0.5\textwidth]{./figures/NGE/MDOver.pdf}
%    \caption{Average overhead running AthenaMP for pilot sizes: 256, 512, 1024 and 2048.}
%\label{fig:MDScal}
%\end{figure}

% For this reason, the second set of the experiments aims to find
%sub-optimal parameters with which we can minimize the trade-off between the size
%of a slot and the time spent in queue waiting for that slot to become available.
%In other words, we aim to minimize the completion time by finding the best
%trade-off between execution time and queue time.
%
%This execution model introduces slot utilization as one of the key factors for
%high-performances. This happens because, in order to minimize the time spent in
%queue, we might asks for slots in advance and, then we could not be able to
%saturate them when they become available. Thus, this strategy requires a new
%functionality that allows the job to receive and execute new events while it is
%already running on the resources. In order to do that we perform the experiments
%by using a new generation executor that implements such functionality.
%
%As last observation, it is important to point out that the percentage of
%utilization of a slot is minor problem with the current implementation because,
%due to the dynamics of the Backfill queue, PanDA has a high probability to
%re-acquire a slot immediately after it has released one\aanote{Are we able to
%quantify this ``immediately''?}.

>>>>

\subsection{Experiments}
\label{sec:ngeExp}

@@

We tested  pilots  with 250, 500, 1000 and 2000 worker nodes and 2 hours
walltime. The time duration is determined by the Titan's walltime policy.
Fig.~\ref{fig:weakScal1a} depicts the average pilot duration, the average
execution time of AthenaMP, and the NGE pilot overhead as function of the pilot
size.

@@

@@

@@

We ran pilots with 256, 512, 1024 and 2048 worker nodes and 3\mtnote{2?} hours
walltime. Fig.~\ref{fig:weakScal2a} depicts the average pilot duration, the
average execution time of five sequential generations of AthenaMP, and the
corresponding overhead. We observe that the difference between the two durations
is more marked than in the previous experiments. Despite this, we notice that
the growth of the overhead is consistent with the increment of the number of
tasks per node for pilots with 256, 512 and 1024 worker nodes, and less than
linear for the pilot with 2048 worker nodes.

@@

@@

Fig.~\ref{fig:strongScala}  shows the average pilot duration and the average
execution time of possibly sequential AthenaMP instances.  We  notice that the
difference between the pilot duration and the AthenaMP execution times is almost
constant for all the pilot sizes, although the overall duration of the pilot
decreases linearly with the pilot size.

@@
